---
title: "Prediciting LSLA with world price index"
author: "Antoine Vuillot"
date: "2023-07-30"
output: pdf_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

# Purpose of the script

In this script, I compute a price index for agricultural lands targeted
by a large-scale land acquisition. The price of a given land is computed
as the average world price of potential agricultural production,
weighted by the crop suitability of the differents crops. This index is
inspired from Berman et al. 2023. World prices data on the period
2000-2021 comes from World Bank data, and crop suitability is from GAEZ
data. Information on land deals come from the Land Matrix Database
(downloaded the 23-09-2023).

Overall this index is a proxy for the profitability of a given
agricultural land. I expect that the higher the index, the more likely
it is for the land to be targeted by a LSLA. Should this relationship be
statistically significant, it should be possible to use price index as
an IV to predict deforestation in the land acquired.

## Loading packages

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(haven)
library(data.table)
library(readxl)
library(sf)
library(RColorBrewer)
library(dplyr)
library(terra)
library(tidyterra)
library(gridExtra)
library(grid)
library(cowplot)
library(scales)
library(mapview)
library(janitor)
library(RCurl) #to download data from URLs

#For TWFE
library(estimatr)
library(lfe)
library(fastDummies)
library(stargazer)
```

## Importing data

```{r}

#Berman et al. 2023
rep_dta = read_dta('berman_al_2023/Replication_data.dta') 
list_price_crop = read_dta('berman_al_2023/list_price_crop.dta') 
wb_prices_annual_berman = read_dta('berman_al_2023/wb_prices_annual.dta') 
suit_crop_gid_gaez = read_dta('berman_al_2023/suit_crop_gid_gaez.dta')
list_crop_main = c("banana", "barley", "cocoa", "coconut", "coffee", "cotton", "maize", "oil palm", "dryland rice", "wetland rice", "sorghum", "soybean", "sugarcane", "tea", "tobacco", "wheat") #List of crops used in the main analysis of Berman et al. 2023

#Annual commodity world prices (nominal)
#https://www.worldbank.org/en/research/commodity-markets
wb_prices_annual_all = read_excel("wb_cmo/CMO-Historical-Data-Annual.xlsx",
                              sheet = "Annual Prices (Nominal)", 
                              skip = 5) %>%
  #Remove the two first lines (description of the variables)
  slice(3:65) %>%
  #Rename variables
  rename("year" = "...1") %>%
  clean_names() %>%
  #Deal with "...", ".." values and transform to numeric all variables
  mutate(across(.cols = everything(),
                .fns = ~ case_when(.x %in% c("…", "..") ~ NA,
                                   TRUE ~ .x))) %>%
  mutate(across(.cols = everything(),
                .fns = ~ as.numeric(.x)))


#Data on land deals (all land deals reported by the LMD after filtering à la Muller et al. 2021)
## Attributes
lmd_muller = fread("data_muller_092023.csv") %>%
  #Filter some deals :
  ## year of intention and year of implementation after 2000
  ## if year of implementation is unknown or deal never implemented, put to NA (null used to be for "never", "" for unknown)
  mutate(year_int = as.numeric(year_int),
         year_impl = as.numeric(
           case_when(year_impl %in% c("", "null") ~ NA,
                               TRUE ~ year_impl)),
         year_cont = as.numeric(
           case_when(year_cont %in% c("", "null") ~ NA,
                               TRUE ~ year_cont))) %>%
  filter(year_int >= 2000 & (is.na(year_impl) | year_impl >= 2000))

##Land polygons
## Note land polygons are defined as disk centered on deal location, whose area equals deals reported area in the LMD. This is necessary as most deals have no polygon reported (Müller et al. 2021).
lmd_T_muller = st_read("Tbuf_muller_092023.geojson") %>%
  filter(loc_id %in% lmd_muller$loc_id) %>%
  mutate(ID = row_number(),
         area_T_km2 = area_T/1e6,
         area_crop_T_km2 = area_crop_T/1e6) 

##An extent of land deals to restrict the computation areas of global rasters
ext_muller = ext(lmd_T_muller)

#mapview(lmd_T_muller)
```

## Download GAEZ data

### List of files' URLs

```{r}

#List of files URLs from the GAEZ website
# Suitability index on the 1981-2010 period, for rainfed water supply (all phases and not all phases), for the same crops as in Berman et al. 2023.
# Both rainfed and rainfed all phases are downloaded to check whether there is any difference in the results obtained.
list_files_si_all_land_1981_2010_gaez = fread('gaez/list_files_gaez_th4_si_AllLand_1981_2010.csv')

#First a list of download URLs : 
## low input level, co2 fertilization, rainfed (water supply)
list_dl_si_gaez_Li_co2_rfed = list_files_si_all_land_1981_2010_gaez %>%
  clean_names() %>%
  mutate(crop = tolower(crop)) %>%
  filter(crop %in% list_crop_main) %>%
  filter(input_level == "Low" 
         & co2_fertilization == "With CO2 Fertilization"
         & water_supply == "Rainfed")

## low input level, co2 fertilization, rainfed (water supply)
list_dl_si_gaez_Li_co2_rfed_all = list_files_si_all_land_1981_2010_gaez %>%
  clean_names() %>%
  mutate(crop = tolower(crop)) %>%
  filter(crop %in% list_crop_main) %>%
  filter(input_level == "Low" 
         & co2_fertilization == "With CO2 Fertilization"
         & water_supply == "Rainfed All Phases")

#Create a list to know which crop corresponds to the file name
df_name2crop = list_dl_si_gaez_Li_co2_rfed %>%
  select(c(name, crop))


```

### Get data and stack rasters in layers

```{r, eval = F}
#Rainfed data
## Define saving directory
dl_dir_rfed = "gaez/si_gaez_Li_co2_rfed"

for (i in 1:nrow(list_dl_si_gaez_Li_co2_rfed))
{
  url = list_dl_si_gaez_Li_co2_rfed[i, download_url]
  #name_lyr = list_dl_si_gaez_Li_co2_rfed[i, name]
  name_file = paste0(list_dl_si_gaez_Li_co2_rfed[i, name], ".tif")
  data = download.file(url,
                      destfile = paste(dl_dir_rfed, name_file, sep = "/"),
                      mode = "wb")
}



#Rainfed all phases data
## Define saving directory
dl_dir_rfed_all = "gaez/si_gaez_Li_co2_rfed_all"

for (i in 1:nrow(list_dl_si_gaez_Li_co2_rfed_all))
{
  url = list_dl_si_gaez_Li_co2_rfed_all[i, download_url]
  #name_lyr = list_dl_si_gaez_Li_co2_rfed[i, name]
  name_file = paste0(list_dl_si_gaez_Li_co2_rfed_all[i, name], ".tif")
  data = download.file(url,
                      destfile = paste(dl_dir_rfed_all, name_file, sep = "/"),
                      mode = "wb")
  
}
```

### Build rasters

```{r}
#Create a list of the files downloaded
list_rast_rfed = list.files("gaez/si_gaez_Li_co2_rfed", 
                            full.names = TRUE)
list_rast_rfed_all = list.files("gaez/si_gaez_Li_co2_rfed", 
                            full.names = TRUE)

#Create a raster where each layers (one crop = one layer) are stacked
##Globally
rast_si_rfed = rast(list_rast_rfed)
rast_si_rfed_all = rast(list_rast_rfed_all)
##Crop to the extent of the lands we consider (less computations)
rast_si_rfed_muller = crop(rast_si_rfed, ext_muller)
rast_si_rfed_all_muller = crop(rast_si_rfed_all, ext_muller)
```

## Compute the price index

### Relative cell suitability

```{r}
#Sum of crop suitability for each raster cell
rast_tot_rfed_muller = app(rast_si_rfed_muller, fun = sum, na.rm = TRUE) %>%
  rename("si_tot" = "sum") %>%
  subst(from = 0, to = NA) #0 values (null or NA suitability for all crops) -> NA to avoid errors

# Compute for each cell the relative suitability index (suitability index of a given crop in a given cell, divided by the total crop suitability in a given cell.)
rast_rsi_rfed_muller = c(rast_si_rfed_muller, rast_tot_rfed_muller) %>%
  transmute(across(names(rast_si_rfed_muller), ~ .x/si_tot))

#Test on smaller raster to check computation steps
# ext = extent(134.4, 134.6,-15.6, -15.4) #extent(112, 159,-54, -9)
# test_si = crop(rast_si_rfed, ext)
# test_tot = app(test_si, fun = sum, na.rm = TRUE) %>%
#   rename("si_tot" = "sum") %>%
#   subst(from = 0, to = NA)
# test_rsi = c(test_si, test_tot) %>%
#   transmute(across(names(rast_si_rfed), ~ .x/si_tot))

#plot(rast_rsi_rfed_muller$sxLr_whe)
```

### Extract relative suitability for each land in our sample

Two possibilities here. From the relative suitability computed for each
crop in each raster cell, it is possible to (1) compute average crop
suitability in the land polygons; (2) assign each pixel to a polygon,
and perform analysis at pixel level.

#### (1) Polygon as unit of analysis

```{r}
#For each land polygon, extract relative suitability values and average it on polygon area
df_rsi_muller_opt1 = extract(x = rast_rsi_rfed_muller, 
                        y = lmd_T_muller,
                        raw = TRUE, 
                        exact = TRUE) %>%
  as.data.frame() %>%
  group_by(ID) %>%
  #Weighted mean of crop suitability among pixels in each land polygon
  summarise(across(.cols = starts_with("sxLr"),
                   .fns = ~ weighted.mean(x = .x, w = fraction, na.rm = TRUE),
                   .names = NULL)) %>%
  #Pivot to longer : 1 row = land+crop
  pivot_longer(cols = starts_with("sxLr"), 
             names_to = "name", 
             values_to = "rsi") %>%
  #Change to clearer crop names
  left_join(df_name2crop, by = c("name")) %>%
  #Add information on land deals
  left_join(lmd_T_muller, by = "ID") %>%
  left_join(lmd_muller, by = c("deal_id", "loc_id")) %>%
  #Select relevant variables
  select(c(region:country, deal_id, loc_id, ID, year_int:year_aban, crop, rsi, contract_farming:livestock_com, geometry)) 


```

#### (2) Pixel as unit of analysis

First let's evaluate the feasibility of this approach.

```{r}
#The resolution of pixels is 0.0833 degrees, or about 9x9km^2 (depending on latitude)
res_rast_opt2 = res(rast_rsi_rfed_muller)

#Area of pixels
## Out of 425 polygons, 61 have an area above 100 km2. It means that most polygons have area below pixel size, so transform the layer of polygons in pixels would lead to extrapolate the grabbed land to the whole pixel.
tbl_T_muller = lmd_T_muller %>%
  summarize(min = min(as.numeric(st_area(geometry)/1e6)),
            max = max(as.numeric(st_area(geometry)/1e6)),
            mean = mean(as.numeric(st_area(geometry)/1e6)),
            med = median(as.numeric(st_area(geometry)/1e6)),
            n_100 = sum(as.numeric(st_area(geometry)/1e6) >= 100),
            n_1 = sum(as.numeric(st_area(geometry)/1e6) >= 1)) %>%
  st_drop_geometry()


```

Then we can transform polygon layer into pixels.

```{r, eval = F}

#Initialize an empty raster to tranform the layer of polygons
rast_ini = rast(crs = crs(rast_rsi_rfed_muller),
                resolution = res(rast_rsi_rfed_muller),
                extent = ext(rast_rsi_rfed_muller))
#Create a raster from land polygons
## Each cell is attributed a polygon ID
### Two options : a cell is assigned a polygon ID if its center is covered (touches = F) or if the polygon is inside the cell (touches = T, less restrictive). I choose to set touches = F  
rast_T_muller = rasterize(x = lmd_T_muller,
                          y = rast_ini,
                          field = "loc_id",
                          fun = "min",
                          background = NA,
                          cover = F,
                          update = F,
                          touches = F)

plot(crop(rast_T_muller, ext(filter(lmd_T_muller, deal_id == 1334))))
test = rast_T_muller %>% as.data.frame(cells = T, na.rm = T)
##Get the cover of each cell
##Eventually, we can then filter cells not enough covered by polygons
rast_T_muller_cover = rasterize(x = lmd_T_muller,
                          y = rast_ini,
                          field = "loc_id",
                          background = NA,
                          cover = T,
                          update = F,
                          touches = F)
df_T_muller_cover = rast_T_muller_cover %>% 
  as.data.frame(cells = T, na.rm = T)
test = df_T_muller_cover %>% filter(cell %in% c(1512024, 1514913))
#Bind RSI and polygon raster
rast_T_rsi_rfed_muller = c(rast_T_muller, rast_rsi_rfed_muller, rast_T_muller_cover)

#Transform it into a dataset
df_rsi_muller_opt2 = rast_T_rsi_rfed_muller %>%
  #Keep pixel ID of initial raster, and keep NA values (background or RSI)
  as.data.frame(cells = T, xy = F, na.rm = F) %>%
  #Keep only cells within a polygon
  filter(is.na(loc_id) == F) %>%
  #Filter pixels not enough covered by a polygon (less than 25%)
  #filter(layer >= 0.25) %>%
  #Pivot to longer : 1 row = land+crop
  pivot_longer(cols = starts_with("sxLr"), 
             names_to = "name", 
             values_to = "rsi") %>%
  #Change to clearer crop names
  left_join(df_name2crop, by = c("name")) %>%
  #Add information on land deals
  left_join(lmd_T_muller, by = "loc_id") %>%
  select(-c(deal_id)) %>%
  left_join(lmd_muller, by = "loc_id") %>%
  #Select relevant variables
  select(c(region:country, deal_id, loc_id, cell, layer, year_int:year_aban, crop, rsi, contract_farming:livestock_com, geometry)) 

#We observe we have 367 pixels corresponding to 200 polygons (characterized by loc_id) left, so less observations than with polygon level analysis.
list_poly_opt2 = unique(df_rsi_muller_opt2$loc_id)
lmd_T_muller_opt2 = lmd_T_muller %>% filter(loc_id %in% list_poly_opt2)
lmd_T_muller_no_opt2 = lmd_T_muller %>% filter(!(loc_id %in% list_poly_opt2))
lmd_muller_opt2 = lmd_muller %>% filter(loc_id %in% list_poly_opt2)
```

### World price (base = 1999)

The deals I consider in the LMD are intended from 2000. This the base
year chosen for world price is 1999.

```{r}
#Select prices for the crop of interests
wb_prices_annual_main = wb_prices_annual_all %>%
  #Select relevant crops
  select(c(year, cocoa, coffee_arabica, coffee_robusta,
           tea_avg_3_auctions, palm_oil, soybeans, barley,
           maize, sorghum, coconut_oil,
           starts_with(c("rice", "wheat", "banana", "sugar")),
           tobacco_us_import_u_v, cotton_a_index)) %>%
  #Compute average of the nominal prices (as with tea_avg_3_auctions in the raw data) for rice, wheat, coffee and banana
  dplyr::rowwise() %>%
  mutate(coffee_avg = mean(c(coffee_robusta, coffee_arabica), na.rm = TRUE),
         .after = "coffee_robusta") %>%
  mutate(rice_avg = mean(c(rice_thai_5_percent, 
                           rice_thai_25_percent, 
                           rice_thai_a_1,
                           rice_viet_namese_5_percent),
                         na.rm = TRUE),
         .after = "rice_viet_namese_5_percent") %>%
  mutate(wheat_avg = mean(c(wheat_us_srw, 
                         wheat_us_hrw),
                       na.rm = TRUE),
       .after = "wheat_us_hrw") %>%
  mutate(banana_avg = mean(c(banana_europe, 
                             banana_us),
                           na.rm = TRUE),
     .after = "banana_us") %>%
  ungroup() %>%
  #Add a world price for dryland and wetland rice (assumed to be similar)
  mutate(dryland_rice = rice_avg,
         wetland_rice = rice_avg,
         .after = "rice_avg")

#Compute price index (base = base_yr)
yr_base = 1999 
wb_prices_annual_main_base = wb_prices_annual_main %>%
  #Build the index : value/base_value*100
  mutate(across(.cols = !c(year),
                .fns = ~.x/.x[year == yr_base]*100)) %>%
  #Select only relevant variables (ie keep average for some crops)
    select(-c("rice_thai_25_percent", "rice_thai_5_percent", 
              "rice_thai_a_1", "rice_avg",
            "rice_viet_namese_5_percent", "wheat_us_srw", "wheat_us_hrw",
            "sugar_eu", "sugar_us", "banana_us", "banana_europe",
            "coffee_arabica", "coffee_robusta")) %>%
  #Make longer to ease matching with RSI dataframe
  pivot_longer(cols = !year,
               names_to = "crop",
               values_to = "wld_price") %>%
  #Keep only year after base_yr
  filter(year >= yr_base) %>%
  #Finally change crop name coherently with GAEZ terminology in df_rsi_muller
  mutate(crop = case_when(crop == "coffee_avg" ~ "coffee",
                          crop == "tea_avg_3_auctions" ~ "tea",
                          crop == "coconut_oil" ~ "coconut",
                          crop == "cotton_a_index" ~ "cotton",
                          crop == "palm_oil" ~ "oil palm",
                          crop == "dryland_rice" ~ "dryland rice",
                          crop == "wetland_rice" ~ "wetland rice",
                          crop == "wheat_avg" ~ "wheat",
                          crop == "banana_avg" ~ "banana",
                          crop == "sugar_world" ~ "sugarcane",
                          crop == "tobacco_us_import_u_v" ~ "tobacco",
                          crop == "soybeans" ~ "soybean",
                          TRUE ~ crop)) 

```

### Compute world price index for each land

Finally knowing world prices for the crops of interest on the period
1999-2022, and relative crop suitability in each land polygon, we can
compute the price index for each land in our sample. Agin two options
are possible : (1) work at polygon level; (2) work at pixel level.

#### (1) Polygon level

```{r}
#Finally we compute price index for each year in each land
df_price_muller_opt1 = df_rsi_muller_opt1 %>%
  #Add the world price of each crop in each year, for each land
  left_join(wb_prices_annual_main_base, by = "crop") %>%
  #For each land and year, compute price index (sum of prices weighted by relative crop suitability)
  group_by(deal_id, loc_id, year) %>%
  summarize(price_idx_loc = sum(rsi*wld_price, na.rm = TRUE)) %>%
  ungroup() %>%
  #Then compute the average price index at deal level 
  group_by(deal_id, year) %>%
  summarize(price_idx_deal = mean(price_idx_loc, na.rm = TRUE)) %>%
  ungroup() %>%
  #Remove the 9 lands with price_index = 0 on the full period (necessarily only rsi = NA)
  filter(price_idx_deal != 0) %>%
  #Add the year of intention, contract and implementation for each land deal
  left_join(select(lmd_muller, 
                   c(deal_id, region, sub_region, country, year_int, year_cont, year_impl)), 
            by = "deal_id") %>%
  #Add a dummy : 1 if the deal is intended/contracted/implemented the year considered
  mutate(dummy_int = ifelse(year == year_int, 1, 0),
         dummy_cont = ifelse(year == year_cont, 1, 0),
         dummy_impl = ifelse(year == year_impl, 1, 0)) %>%
  #Reorder variables
  select(c(region,country, sub_region, deal_id, year, price_idx_deal, year_int:dummy_impl))


```

#### (2) Pixel level

```{r, eval = F}
#Finally we compute price index for each year in each pixel
df_price_muller_opt2 = df_rsi_muller_opt2 %>%
  #Add the world price of each crop in each year, for each pixel
  left_join(wb_prices_annual_main_base, by = "crop") %>%
  #For each pixel and year, compute price index (sum of prices weighted by relative crop suitability)
  group_by(deal_id, loc_id, cell, year) %>%
  summarize(price_idx_pix = sum(rsi*wld_price, na.rm = TRUE)) %>%
  ungroup() %>%
  #Remove the 22 cells with price_index = 0 on the full period (necessarily only rsi = NA)
  filter(price_idx_pix != 0) %>%
  #Add the year of intention, contract and implementation for each land deal
  left_join(select(lmd_muller, 
                   c( loc_id, region, sub_region, country, year_int, year_cont, year_impl)), 
            by = "loc_id") %>%
  #Add a dummy : 1 if the deal is intended/contracted/implemented the year considered
  mutate(dummy_int = ifelse(year == year_int, 1, 0),
         dummy_cont = ifelse(year == year_cont, 1, 0),
         dummy_impl = ifelse(year == year_impl, 1, 0)) %>%
  #Reorder variables
  select(c(region, country, sub_region, deal_id, loc_id, cell, year, price_idx_pix, year_int:dummy_impl))


```

## Analysis

### Visual evidences

#### Define plot datasets : subregional and world level

```{r}
df_plot_subreg_opt1 = df_price_muller_opt1 %>%
  group_by(sub_region, year) %>%
  #Count the number of deal intended/contracted/implemented in each sub-region, each year
  # Compute the average price index across deals for each sub-region/year
  summarize(n_int = sum(dummy_int, na.rm = TRUE),
            n_cont = sum(dummy_cont, na.rm = TRUE),
            n_impl = sum(dummy_impl, na.rm = TRUE),
            idx_avg = mean(price_idx_deal, na.rm = TRUE)) %>%
  ungroup()
  
# Same at world level
df_plot_wld_opt1 = df_price_muller_opt1 %>%
  group_by(year) %>%
    summarize(n_int = sum(dummy_int, na.rm = TRUE),
            n_cont = sum(dummy_cont, na.rm = TRUE),
            n_impl = sum(dummy_impl, na.rm = TRUE),
            idx_avg = mean(price_idx_deal, na.rm = TRUE)) %>%
  ungroup() 
```

#### Plot figures : time evolution of land deals, world prices and price index index.

Evolution of world prices, for a subset of crops. Overall, the world
price of commodities considered increase from 2000 up to around 2010,
then decrease and increase again from 2020.

```{r}
#Define a list of crops to reduce the number of curves to display
#Note dryland and wetland rice follow same evolution exactly
lst_crop = c("oil palm", "soybean", "maize", "sorghum", "dryland rice", "wheat", "sugarcane")
fig_wld_prices = ggplot(data = subset(wb_prices_annual_main_base, crop %in% lst_crop),
                        aes(x = year, y = wld_price, col = crop)) %>%
  + geom_point() %>%
  + geom_line() %>%
  + scale_color_brewer(name = "Crops", type = "seq", palette = "Dark2") %>%
  + labs(title = 'Evolution of crop world prices',
         y = "Price index (base = 1999)",
       x = 'Year') %>%
  + theme_minimal()
fig_wld_prices

ggsave(plot = fig_wld_prices,
       filename = "figures/fig_wld_prices.jpeg",
       device = "jpeg",
       width = 9,
       height = 6)

```

Evolution of price index in the different sub-regions (average of
parcels' price indices). The agricultural value of land considered,
proxied by the index, increase from 2000 to around 2008. After a fall in
2009 it increases again with a peak around 2010. The price index then
decreases and increase again from 2019. Interestingly the evolution is
comparable across sub-regions.

```{r}
fig_idx_subreg_opt1 = ggplot(df_plot_subreg_opt1,
                 aes(x = year, y = idx_avg, col = sub_region)) %>%
  + geom_point() %>%
  + geom_line() %>%
  + scale_color_manual(name = "Sub-regions",
                       values = brewer.pal(n = 6, name = "Dark2")) %>%
  + labs(title = 'Evolution of price index in the different sub-regions',
         subtitle = "Analysis at polygon level",
         y = "Price index (base = 1999)",
       x = 'Year') %>%
  + theme_minimal()
fig_idx_subreg_opt1

ggsave(plot = fig_idx_subreg_opt1,
       filename = "figures/fig_idx_subreg_poly.jpeg",
       device = "jpeg",
       width = 9,
       height = 6)
```

Evolution of land deals and price index in the world. Up to 2015, it
seems that the evolution in the number of deals contracted or intended
is correlated with the price index (less clear for implementation) : an
increase up to 2010 then a decrease. The correlation after 2015 is less
clear. Especially the rise of the price index from 2019 is not followed
by a rise in land deals. This can be due to the moratoria on land deals
after 2010 in different countries (e.g Indonesia, see Land Matrix
Initiative 2021 analytical report).

```{r}

coef = .2
fig_lsla_idx_wld_opt1 = ggplot(df_plot_wld_opt1,
                 aes(x = year)) %>%
  + geom_point(aes(y = n_int, color = "Intended")) %>%
  + geom_line(aes(y = n_int, color = "Intended")) %>%
  + geom_point(aes(y = n_cont, color = "Contracted")) %>%
  + geom_line(aes(y = n_cont, color = "Contracted")) %>%
  + geom_point(aes(y = n_impl, color = "Implemented")) %>%
  + geom_line(aes(y = n_impl, color = "Implemented")) %>%
  + geom_point(aes(y = coef*idx_avg, color = "Index")) %>%
  + geom_line(aes(y = coef*idx_avg, color = "Index")) %>%

  + scale_y_continuous(name = 'Amount', sec.axis = sec_axis(trans = ~./coef, name = 'Price index (base year = 1999)')) %>%
  + scale_color_manual(name = "",
                       values = c("Intended" = "grey80",
                                  "Contracted" = "grey50",
                                  "Implemented" = "grey20",
                                  "Index" = "gold")) %>%
  + labs(title = 'Co-evolution of price index and land deals over time',
         subtitle = "World, analysis at polygon level",
       x = 'Year') %>%
  + theme_minimal()
fig_lsla_idx_wld_opt1

ggsave(plot = fig_lsla_idx_wld_opt1,
       filename = "figures/fig_lsla_idx_wld_poly.jpeg",
       device = "jpeg",
       width = 9,
       height = 6)
```

Same graph in the different sub-regions. Due to the low number of deals
reported, comparison is not relevant in Melanesia and Southern Europe.
In Eastern Europe, the number of deals intended/contracted/implemented
does not seem to follow the price index. This relationship is more clear
in South-eastern Asia and SSA, though some lag can be observed between
the peak in price index and in the number of deals. In both sub-regions,
we observe a fall in the number of deals with the drop in price index.
However the increase in the price index from 2019 is not followed by an
increase in land deals, as highlighted at world level. Finally, the
figure for Latin America is less clear to interpret. We observe a major
peak in 2008 for land deals, while the main price peak is in 2011.

```{r}

#Define a function to plot co-evolution of land deals and price index in the different sub-regions, in a same graph. 
fn_fig_lsla_idx_subreg_opt1 = function(df_subreg, coef)
  {
  list_fig_subreg = list()
  list_sub_region = unique(df_subreg$sub_region)
  coef = coef
  
  for(i in 1:length(list_sub_region))
  { 
  roi = list_sub_region[i]
  df = filter(df_subreg, sub_region == roi)
  fig_i = ggplot(data = df,
                 aes(x = year)) %>%
  + geom_point(aes(y = n_int, color = "Intended")) %>%
  + geom_line(aes(y = n_int, color = "Intended")) %>%
  + geom_point(aes(y = n_cont, color = "Contracted")) %>%
  + geom_line(aes(y = n_cont, color = "Contracted")) %>%
  + geom_point(aes(y = n_impl, color = "Implemented")) %>%
  + geom_line(aes(y = n_impl, color = "Implemented")) %>%
  + geom_point(aes(y = coef*idx_avg, color = "Index")) %>%
  + geom_line(aes(y = coef*idx_avg, color = "Index")) %>%

  + scale_y_continuous(name = 'Amount of reported steps', sec.axis = sec_axis(trans = ~./coef, name = 'Price index (base year = 1999)')) %>%
  + scale_color_manual(name = "",
                       values = c("Intended" = "grey80",
                                  "Contracted" = "grey50",
                                  "Implemented" = "grey20",
                                  "Index" = "gold")) %>%
  + labs(subtitle = paste0(roi, "\n", sum(df$n_int), " intended, ", sum(df$n_cont), " contracted, ", sum(df$n_impl), " implemented")) %>%
  + theme_minimal()
  
    list_fig_subreg[[i]] = fig_i
    
  }
  
  mplot = plot_grid(plotlist = list_fig_subreg,
                        align = "hv",
                        nrow = 3,
                        ncol = 2,
                        labels = "AUTO"
                        )

#Adding a common x and y axis

y.grob <- textGrob("Number of steps reported",
                 gp=gpar(fontface = "bold", fontsize=15), rot=90)
x.grob <- textGrob("Year after treatment",
                 gp=gpar(fontface = "bold", fontsize=15))
title.grob <- textGrob("Co-evolution of price index and land deals, at polygon level",
                 gp=gpar(fontface = "bold", fontsize=17))
# #Building the final figure
fig = grid.arrange(arrangeGrob(mplot, left = y.grob, bottom = x.grob, top = title.grob))

ggsave(plot = fig,
       filename = "figures/fig_lsla_idx_subreg_poly.jpeg",
       device = "jpeg",
       width = 18,
       height = 12)

return(fig)
  
}

#Call the function and display the graph
fig_lsla_idx_subreg_opt1 = fn_fig_lsla_idx_subreg_opt1(df_subreg = df_plot_subreg_opt1, coef = .1)
fig_lsla_idx_subreg_opt1
```

### Testing the IV

Outcome : predicting the fact the deal/pixel is implemented

```{r}
#A linear model : whether the deal has been implemented or not, regressed on price index. Do it for SSA and SEA and World

#A dataframe to estimate the model
df_est1_wld_poly = df_price_muller_opt1 %>%
  #remove deals with unknown implementation date, and restrict to before COVID period
  filter(is.na(year_impl) == F & year <= 2020) %>%
  #Add a dummy for treatment : 1 once the deal is implemented, 0 before
  group_by(deal_id) %>%
  mutate(is_impl = as.numeric(year >= year_impl)) %>%
  ungroup()
df_est1_wld_pix = df_price_muller_opt2 %>%
  #remove deals with unknown implementation date, and restrict to before COVID period
  filter(is.na(year_impl) == F & year <= 2020) %>%
  #Add a dummy for treatment : 1 once the deal is implemented, 0 before
  group_by(cell) %>%
  mutate(is_impl = as.numeric(year >= year_impl)) %>%
  ungroup()
#Estimate the models
##World
### Polygon level -> sig, +
lm1_wld_opt1 = lfe::felm(formula = is_impl ~ price_idx_deal | deal_id + year | 0 ,
                        data = df_est1_wld_poly)
summary(lm1_wld_opt1)
### Pixel level -> sig, +
lm1_wld_opt2 = lfe::felm(formula = is_impl ~ price_idx_pix | cell + year | 0 | deal_id ,
                        data = df_est1_wld_pix)
summary(lm1_wld_opt2)
##SEA
### Polygon -> non sig
lm1_sea_opt1 = lfe::felm(formula = is_impl ~ price_idx_deal | deal_id + year | 0 ,
                        data = filter(df_est1_wld_poly, sub_region == "South-eastern Asia"))
summary(lm1_sea_opt1)
### Pixel -> non sig
lm1_sea_opt2 = lfe::felm(formula = is_impl ~ price_idx_pix | cell + year | 0 | deal_id ,
                        data = filter(df_est1_wld_pix, sub_region == "South-eastern Asia"))
summary(lm1_sea_opt2)
##SSA
### Polygon -> sig, +
lm1_ssa_opt1 = lfe::felm(formula = is_impl ~ price_idx_deal | deal_id + year | 0,
                        data = filter(df_est1_wld_poly, sub_region == "Sub-Saharan Africa"))
summary(lm1_ssa_opt1)
### Pixel -> sig, +
lm1_ssa_opt2 = lfe::felm(formula = is_impl ~ price_idx_pix | cell + year | 0 | deal_id ,
                        data = filter(df_est1_wld_pix, sub_region == "Sub-Saharan Africa"))
summary(lm1_ssa_opt2)
```

Outcome : the number of deal implemented at sub-regional level

```{r}
#Create dataframe
df_est2_wld_poly = df_price_muller_opt1 %>%
   #remove deals with unknown implementation date, and restrict to before COVID period
  filter(is.na(year_impl) == F & year <= 2020) %>%
  group_by(sub_region, year) %>%
  summarize(avg_price_idx = mean(price_idx_deal),
         n_impl = sum(dummy_impl)) %>%
  ungroup()
df_est2_wld_pix = df_price_muller_opt2 %>%
   #remove deals with unknown implementation date, and restrict to before COVID period
  filter(is.na(year_impl) == F & year <= 2020) %>%
  group_by(sub_region, year) %>%
  summarize(avg_price_idx = mean(price_idx_pix),
         n_impl = sum(dummy_impl)) %>%
  ungroup()

#Estimate linear models
##SEA 
n_sea_poly = length(unique(filter(df_est1_wld_poly, sub_region == "South-eastern Asia")$deal_id))
n_sea_pix = length(unique(filter(df_est1_wld_pix, sub_region == "South-eastern Asia")$cell))
### Poly --> sig, +
lm2_sea_opt1 = felm(formula = n_impl ~ avg_price_idx | sub_region | 0 | 0 ,
                        data = filter(df_est2_wld_poly, sub_region == "South-eastern Asia"))
summary(lm2_sea_opt1)
lm2_sea_opt2 = felm(formula = n_impl ~ avg_price_idx | sub_region | 0 | 0 ,
                        data = filter(df_est2_wld_pix, sub_region == "South-eastern Asia"))
summary(lm2_sea_opt2)
##SSA
n_ssa_poly = length(unique(filter(df_est1_wld_poly, sub_region == "Sub-Saharan Africa")$deal_id))
n_ssa_pix = length(unique(filter(df_est1_wld_pix, sub_region == "Sub-Saharan Africa")$cell))
### Poly --> sig, +
lm2_ssa_opt1 = felm(formula = n_impl ~ avg_price_idx | sub_region  | 0 | 0 ,
                        data = filter(df_est2_wld_poly, sub_region == "Sub-Saharan Africa"))
summary(lm2_ssa_opt1)
### Pixel --> non-sig
lm2_ssa_opt2 = felm(formula = n_impl ~ avg_price_idx | sub_region  | 0 | 0 ,
                        data = filter(df_est2_wld_pix, sub_region == "Sub-Saharan Africa"))
summary(lm2_ssa_opt2)
```
